Computing exact restricted isometry constants via\\ mixed integer semidefinite programming

### 2015-01-02 RIP-MISDP-Paper/Paper_v1.tex
some style changes for title

\title{Computing exact restricted isometry constants via mixed integer semidefinite programming}
\author[tud]{T. Gally}
\ead{gally@mathematik.tu-darmstadt.de}
\author[tud]{M. E. Pfetsch}
\ead{pfetsch@mathematik.tu-darmstadt.de}
\address[tud]{Technische Universit\"at Darmstadt, Department of Mathematics, Dolivostra\ss e 15, 64293 Darmstadt, Germany}

>>>>

\title{Computing exact restricted isometry constants via\\ mixed integer semidefinite programming}
\author[tud]{Tristan Gally}
\ead{gally@mathematik.tu-darmstadt.de}
\author[tud]{Marc E. Pfetsch}
\ead{pfetsch@mathematik.tu-darmstadt.de}
\address[tud]{Technische Universit\"at Darmstadt, Department of Mathematics,\\ Dolivostra\ss e 15, 64293 Darmstadt, Germany}
